---
title: "HubPub: Help with publication of Hub packages"
author:
- name: Kayla Interdonato
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
- name: Martin Morgan
  affiliation: Roswell Park Comprehensive Cancer Center, Buffalo, NY
date: "`r Sys.Date()`"
output:
    BiocStyle::html_document:
        toc: true
        toc_float: true
package: HubPub
vignette: >
  %\VignetteIndexEntry{HubPub: Help with publication of Hub packages}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

# Introduction

`HubPub` provides users with functionality to help with the _Bioconductor_ Hub
structures. The package provides the ability to create a skeleton of a Hub
style package that the user can then populate with the necessary information.
There are also functions to help add resources to the Hub pacakge metadata
files as well as publish data to the _Bioconductor_ S3 bucket.

# Installation
Install the most recent version from Bioconductor:

```{r bioconductor, eval = FALSE}
if(!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("HubPub")
```

Then load `HubPub`:

```{r load, message = FALSE}
library(HubPub)
```

# HubPub

## Creating a Hub styled package

The `create_pkg()` function creates the skeleton of a package that follows the
guidelines for a _Bioconductor_ Hub type package. Once the function is
executed it is expected that the developer will go through and make any
necessary changes as the package takes shape. 

NOTE: This function is intended for a developer that has not created the
package yet. If the package has already been created, then this function 
will not be benefit the developer. There are a couple other functions in this
package that deal with resources that might be helpful, more on these later in
the vignette.

`create_pkg()` requires a path to where the packages is to be created and the type
of package that should be created ("AnnotationHub" or "ExperimentHub"). There is
also a variable `use_git` that indicates if the package should be set up with git (default is `TRUE`).

```{r create}
fl <- tempdir()
create_pkg(paste0(fl, "/examplePkg"), "ExperimentHub")
```

Once the package is created the developer can go through and make any changes to
the package. For example, the DESCRIPTON file contains very basic
requirements but the developer should go back and fill in the 'Title:' and
'Description:' fields.

More information about what are the requirements and content for a Hub style
package the developer can look at the "Creatin A Hub Package" vignette from
`r Biocpkg("AnnotationHub")`.

## Adding a resource to the metadata file

## Publishing the resource to AWS S3

# Session Information

```{r session_info}
sessionInfo()
```
